%\documentclass[11pt,reqno]{amsart}
\documentclass[11pt,reqno]{article}
\usepackage[margin=.8in, paperwidth=8.5in, paperheight=11in]{geometry}
%\usepackage{geometry}                % See geometry.pdf to learn the layout options. There are lots.
%\geometry{letterpaper}                   % ... or a4paper or a5paper or ... 
%\geometry{landscape}                % Activate for for rotated page geometry
%\usepackage[parfill]{parskip}    % Activate to begin paragraphs with an empty line rather than an indent7
\usepackage{graphicx}
\usepackage{pstricks}
\usepackage{amssymb}
\usepackage{epstopdf}
\usepackage{amsmath}
\usepackage{subfigure}
\usepackage{caption}
\pagestyle{plain}
%\renewcommand{\topfraction}{0.3}
%\renewcommand{\bottomfraction}{0.8}
%\renewcommand{\textfraction}{0.07}
\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}

\title{Real Analysis $\mathbb{I}$: \\ Assignment 5}
\author{Andrew Rickert}
\date{Started: April 20, 2011 \\ \hspace{1pt} Ended: April ??  2011}                                           % Activate to display a given date or no date

\begin{document}
\maketitle


% Page 1
\begin{flushleft} 
\textbf{Class 18.100B} - Problem 1\\
\rule{500pt}{1pt}\\
\end{flushleft} 

First we show that $X$ being closed implies completeness. Since a Cauchy sequence in $X$ is a Cauchy sequence in $M$ where $X$ is a subset and $M$ is complete we know that the sequence converges. Since the sequence consists of points of $X$ then every neighborhood of the point of convergence contains elements of $X$, that is it is a limit point. Because $X$ is closed it contains the limit point so every Cauchy sequence in $X$ converges to a point in $X$ and so the set is complete.\\
\indent For the inverse we need to show that if $X$ is complete then $X$ is closed. Consider a limit point $x \in X$. By the definition of a limit point there is $p_1 \in X$ such that $d(p_1,x) < \frac{1}{2}$. Similarly we may find a $p_2 \in X$ such that $d(p_2,x) < \frac{1}{4}$ and so on. In this way we produce a sequence in $X$ such that $d(p_n,x) < \frac{1}{2^n}$. This sequence converges to a point $p$. Since every convergent sequence is a Cauchy sequence by a theorem in Rudin and $X$ is complete the point of convergence must be in $X$ so $p \in X$ and $X$ is closed.

\vspace{15pt}
\begin{flushleft} 
\textbf{Class 18.100B} - Problem 2\\
\rule{500pt}{1pt}\\
\end{flushleft} 

\noindent Part a) We need to show that if $(x_{2n})$ and $(x_{2n-1})$ both converge to the same limit then $(x_n)$ converges and vice versa. Concluding that $(x_{2n})$ and $(x_{2n-1})$ converge when $(x_n)$ follows from the fact that every subsequence of convergent series converges to the same limit. The other conclusion that $(x_n)$ converges if $(x_{2n})$ and $(x_{2n-1})$ do goes as follows.\\
\indent Since $(x_{2n})$ converges there exists an $N_1$ such that for given $\epsilon$ we have $|x_{2n}-x'| < \epsilon$ for $n > N_1$ where $x'$ is the limit. Similarly for $(x_{2n-1})$ we have $N_2$ such that  $|x_{2n-1}-x'| < \epsilon$ for $n > N_2$. If we take $N = \text{max} (2N_1,2N_2)$ then for $n > N$ we have $|x_n -x'| < \epsilon$ since either $x_n = x_{2n'}$ or $x_n = x_{2n'-1}$ for some $n'$. This shows that $(x_n)$ converges by virtue of the convergence of $(x_{2n})$ and $(x_{2n-1})$.\\

\noindent Part b) Now we need to show that $(x_n)$ converges if $(x_{2n})$,$(x_{2n-1})$, and $(x_{5n})$ all converge. We suppose that $\lim_{n \to \infty}(x_{2n}) = \alpha$ and, $\lim_{n \to \infty}(x_{2n-1}) = \beta$ and $\alpha \neq \beta$. \\
\indent There is a subsequence of $(x_{5n})$ that is a subsequence of $(x_{2n})$ since if $n = 2k$ we have $5n = 5(2k) = 2(5k) = 2j$ where $j = 2k$. So for even $n$, then subsequence of $(x_{5n})$ is a subsequence of $(x_{2n})$. Since every subsequence of a convergent sequence converges to the same limit then we have $\lim_{n \to \infty}x_{5n} = \lim_{k \to \infty} x_{5(2k)} = \lim_{k \to \infty}x_{2(2k)} = \lim_{n \to \infty}x_{2n} = \alpha$.\\
\indent Similarly there is a subsequence of $(x_{5n})$ that is a subsequence of $(x_{2n-1})$   since if $n = 2k-1$ then $5n = 5(2k-1) = 10k -5 = 2(5k-2)-1= 2j-1$ where $j=5k-2$. By the same reasoning as the previous paragraph we get $\lim_{n \to \infty}x_{5n} = \lim_{k \to \infty} x_{5(2k-1)} = \lim_{k \to \infty}x_{2(2k-1)-1} = \lim_{n \to \infty}x_{2n-1} = \beta$. This shows that $\alpha = \beta$ contrary to our hypothesis so  $(x_{2n})$ and $(x_{2n-1})$ must converge to the same limit and by part a this must be the limit of the origin sequence $(x_n)$.

\vspace{15pt}
\begin{flushleft} 
\textbf{Class 18.100B} - Problem 3\\
\rule{500pt}{1pt}\\
\end{flushleft} 

We need to show that  $\limsup (x_n + y_n) \le \limsup x_n + \limsup y_n$. First we point out that the set of all subsequences is closed which means by a theorem of Rudin that the supremum is included in the set. This means there exists a subsequence that limits to this value which is the limit supremum. So, if $(x_{m_k})$ is any subsequence and $(x_{n_k})$ is a sequence that limits to the limit supremum then  $\lim_{k \to \infty}(x_{m_k}) \le \lim_{k \to \infty}(x_{n_k})$ by the definition of the upper limit.\\
\indent if we let $(x_{m_k} + y_{m_k})$ be the limit supremum sequence of ($x_n + y_n$)  and $(x_{n_k})$ and $(y_{n_k})$ be the limit supremum sequences of their individual sequences respectively then we have the following calculation that gives the result
\begin{eqnarray*}
\limsup (x_n + y_n) & = & \lim_{k \to \infty}(x_{m_k} + y_{m_k}) \\
			      & = & \lim_{k \to \infty} x_{m_k} + \lim_{k \to \infty}y_{m_k}\\
                                          & \le & \lim_{k \to \infty} x_{n_k} + \lim_{k \to \infty}y_{n_k}\\
			      & = & \limsup \; x_n + \limsup \;y_n
\end{eqnarray*}

The observation that if $(x_{m_k})$ is any sequence then $\lim_{k \to \infty}(x_{m_k}) \ge \liminf\; x_n$ allows the reasoning in the previous paragraphs to show the result for the $\liminf$.\\
\indent Now we need to show that if $(x_n)$ converges then we get equality instead of the inequality. Since $x_n$ converges by hypothesis every subsequence converges to the same limit. No suppose that $\{n_k\}$ is a set of integers such that the subsequence of $(y_n)$ converges to the $\limsup$. That is, $\lim_{k \to \infty}y_{n_k} = \limsup y_n$. If we use the same set of integers for $(x_n)$ then we have the subsequence $(x_{n_k} + y_{n_k} )$. Since by definition the limit supremum is the least upper bound of subsequential limits we have the following \[\limsup(x_n + y_n) \ge \lim_{k \to \infty}(x_{n_k} + y_{n_k})\]
Since $x_n$ converges and every subsequence converges to the same limit, a limit supremum sequence of this sequence must equal to same limit as any subsequence. So we have 
\begin{eqnarray*}
\limsup(x_n + y_n) & \ge & \lim_{k \to \infty}(x_{n_k} + y_{n_k})\\
                                  & = & \lim_{k \to \infty}x_{n_k} + \lim_{k \to \infty}y_{n_k}\\
                                  & = & \limsup x_n + \lim_{k \to \infty}y_{n_k} \; \text{by the previous comment}\\
                                 & = & \limsup x_n + \limsup y_n \;  \text{by the definition of the subsequence}\;\{n_k \}
\end{eqnarray*}
 Since both $\limsup(x_n + y_n) \ge \limsup x_n + \limsup y_n$ and $\limsup(x_n + y_n) \le \limsup x_n + \limsup y_n$ from the previous part of the problem we have  $\limsup(x_n + y_n) = \limsup x_n + \limsup y_n$. The reasoning for the $\liminf$ is the same with appropriate inequality signs reversed.

\vspace{15pt}
\begin{flushleft} 
\textbf{Class 18.100B} - Problem 4\\
\rule{500pt}{1pt}\\
\end{flushleft} 

Let's quickly show that if $\liminf x_n = \limsup x_n = x'$ then $\lim_{n \to \infty} x_n = x'$. Suppose the hypothesis is given then from a theorem in Rudin if there is an $x > \limsup x_n$ then there is an $N_1$ such that $x_n < x$. For the infimum we have the fact that if $x < \liminf x_n$ then there is an $N_2$ such that $x_n > x$. If we denote $x^* = \liminf x_n = \limsup x_n$ then we let $x = x^* + \epsilon$ for the limit supremum and $x = x^* - \epsilon$ and take $N = \text{max}\;(N_1,N_2)$ and we have $x^* - \epsilon < x_n < x^* + \epsilon$ for $n > N$. This is to say that the sequence converges to the common value for the limit supremum and limit infimum.\\
\indent From looking at the inequality we are intended to prove $\liminf x_n \le \liminf a_n \le \limsup a_n \le \limsup x_n$ we can see by the result just shown that if $x_n \to x$ then $a_n \to x$. This is so because if  $x_n \to x$ then $\liminf x_n = \limsup x_n$ since they are both subsequences of a convergent sequence. Also if $\liminf a_n < \limsup a_n$ then we violate the inequality we are suppose to prove because then we have $x \le \liminf a_n < \limsup a_n \le x$ which is impossible. From our previous remarks $\liminf a_n = \limsup a_n$ shows $a_n \to a$ so we have $x \le a \le x$ which implies that $x = a$ or $a_n \to x$ if $x_n \to x$. So our goal becomes to try to show the inequality and the main result will follow.\\
\indent Because $ \liminf a_n < \limsup a_n $ follows directly from the definitions of the upper and lower limits and greatest/least upper bounds we will focus on showing $\limsup a_n < \limsup x_n$ and then comment on how the result can be adapted to the lower limit.\\
\indent We start as suggested in the problem by letting $x^* = \limsup x_n$ and $K = \{ k \in \mathbb{N} \; | \; x_k \ge x^* + \epsilon \}$. We note that $K$ is finite for otherwise we would have an infinite number of points in the interval $[x^* + \epsilon, \text{sup} \; x_n]$. This compact set will have a limit point and so there is a subsequence whose limit is $\ge x^* + \epsilon$ contrary to the definition of $x^*$. Next we define $\mathcal{S}_n = \{ i \in \mathbb{N} \; | \; i \in K \; \text{and} \; i \le n\}$ and $\mathcal{T}_n = \{ i \in \mathbb{N} \; | \; i \notin K \; \text{and} \; i \le n\}$. Either $x_k \ge x^* + \epsilon$ or $x_k < x^* + \epsilon$ for all $k \in \mathbb{N}$ so $x_n \in \mathcal{S}_n$ or $x_n \in \mathcal{T}_n$. $\mathcal{S}_n$ only includes points in $K$ so we know that it is finite because $K$ is. This means that we can always rearrange the sum $\sum_n x_n$ so that the terms with indices in $\mathcal{S}_n$ will be at the front because a finite rearrangement does not change the value of a series. Since the other terms must be $\mathcal{T}_n$ we have the sum $\sum_n x_n = s_n + t_n$ where $s_n = \sum_{i \in \mathcal{S}_n}x_i$ and $t_n = \sum_{i \in \mathcal{T}_n}x_i$. \\
\indent By the definition of $\mathcal{T}_n$ we know that if $k \in \mathcal{T}_n$ then $k \notin K$ so $x_k < x^* + \epsilon$. So $t_ n = \sum_{k \in \mathcal{T}_n} x_k < n(x^* + \epsilon)$ 
which gives $\frac{t_n}{n} < x^* + \epsilon$. This gives $\limsup \frac{t_n}{n} \le x^* + \epsilon$. Also, because $\mathcal{S}_n$ is finite we know that the sum of all $x_k$ with $k \in K$ is a finite value as well and so is an upper bound $S$ on the sum $s_n$. Therefore we have $\frac{s_n}{n} < \frac{S}{n}$ for all $n$. This gives $\limsup \frac{s_n}{n} = 0$.\\
\indent Using the result from the previous problem we derive:
\begin{equation}
\limsup a_n = \limsup(\frac{s_n}{n} + \frac{t_n}{n}) \le  \limsup \frac{s_n}{n} +\limsup \frac{t_n}{n} = 0 + x^* + \epsilon
\end{equation}

We have that $\limsup a_n \le x^* + \epsilon$ but $\epsilon$ is arbitrary so $\limsup a_n \le x^*$. Otherwise we would have $\limsup a_n - x^* = \beta > 0$ then let $\epsilon = \frac{\beta}{2}$ and we violate the inequality  $\limsup a_n \le x^* + \epsilon$. Since $x^* = \limsup x_n$ we have $\limsup a_n \le \limsup x_n$ as was to be shown. By defining $K' = \{ k \in \mathbb{N} \; | \; x_k \le x' + \epsilon \}$ with $x' = \liminf x_n$ and repeating the previous arguments using $
\liminf$ instead of $\limsup$ we get $\liminf x_n \le \liminf a_n$ which completes the inequality.\\
\indent A counterexample to show that if $a_n$ may converge but $x_n$ will not is the sequence $x_n = (1,0,1,0,1,0,1,\cdots)$. From inspection it is clear that $a_n = (1,\frac{1}{2},\frac{2}{3},\frac{1}{2},\frac{3}{5},\frac{1}{2},\frac{4}{7},\cdots)$ which is to say $a_n = \frac{1}{2}$ for even indices and $a_n = \frac{n}{2n-1}$ for odd indices. From this we see $a_n \to \frac{1}{2}$ and that $x_n$ does not converge.

\vspace{15pt}
\begin{flushleft} 
\textbf{Class 18.100B} - Problem 5\\
\rule{500pt}{1pt}\\
\end{flushleft} 

Our first step is to show that the sequence $x_{n+1} = 1 - \sqrt{1-x_n}$ is bounded. We are given that $1 > x_1 > 0$. Now assume that $1 > x_n > 0$. Then we have
\begin{eqnarray*}
 0 < 1 - x_n < 1 &\implies& 1 > \sqrt{1- x_n} > 0 \\
                          &\implies& -1 < -\sqrt{1-x_n} < 0 \\
                          &\implies& 0 < 1 - \sqrt{1-x_n} < 1 \\
                          &\implies& 0 < x_{n+1} < 1
\end{eqnarray*}
This completes the induction and shows that $x_n$ is bounded by 0 and 1. We can now show that the sequence decreases. Since $x_n >$ we have the following calculation
\begin{eqnarray*}
x_n > 0 & \implies & 1 > 1 - x_n \\
	 & \implies & 1-x_n > (1-x_n)^2 \quad \text{since $1 > x_n$ implies $1 - x_n > 0$} \\
	 & \implies & x_n > 1 - \sqrt{1-x_n} \\
 	& \implies & x_n > x_{n+1} \\
\end{eqnarray*}
This shows that $(x_n)$ is strictly decreasing. Since the sequence is both decreasing and bounded below we know from a theorem in Rudin that the sequence converges. This allows us to perform the following calculation.
\[
x = \lim_{n \to \infty} x_{n+1} = \lim_{n \to \infty} 1 - \sqrt{1 - x_n} = 1- \sqrt{1 - x}
\]

So $x = 1 - \sqrt{1-x}$ where $x = \lim_{n \to \infty} x_{n+1}$, solving the equation for $x$ yields $x = 0$ as was to be shown.\\
\indent The last part of the problem is to show that $\lim_{n \to \infty}\frac{x_{n+1}}{x_n} \to \frac{1}{2}$. We perform to the following calculation to get an appropriate form for the desired limit.
\begin{eqnarray*}
x_{n+1} &=& 1 - \sqrt{1 - x_n} \\
1 - x_{n+1} &=& \sqrt{1 - x_n} \\
(1 - x_{n+1})^2 &=& 1 - x_n \quad \text{Since $1 - x_n > 0$ implies that $1 - x_n \neq 0$}\\
1 - 2 x_{n+1} + x_{n+1}^2 &=& 1 - x_n \\
2 x_{n+1} - x_{n+1}^2 &=& x_n \\
\frac{x_{n+1}}{x_n}(2 - x_{n+1})&=& 1 \\
\frac{x_{n+1}}{x_n}&=& \frac{1}{2 - x_{n+1}} \\
\end{eqnarray*}
 From this we see that \[\lim_{n \to \infty} \frac{x_{n+1}}{x_n} = \lim_{n \to \infty}\frac{1}{2-x_{n+1}} = \frac{1}{2}\] since as was already established $\lim_{n \to \infty} x_{n+1} = 0$. This completes the problem.
\vspace{15pt}
\begin{flushleft} 
\textbf{Class 18.100B} - Problem 6\\
\rule{500pt}{1pt}\\
\end{flushleft} 

Part a) We need to show that the Greek definition of the golden ratio corresponds to the equation $\Phi^2 = \Phi + 1$. \\
\indent According to the Greek definition we have \[a = b + c\] since the side $A$ is broken up into $B$ and $C$ where $a,b$ and $c$ are their respective lengths. We are also give that the ratio of the length of the whole $A$ to the largest part $B$ is the same as the ratio of the largest part $B$ to the smaller part $C$. This gives the relationship \[\frac{a}{b} =\frac{b}{c}\] From this we derive \begin{equation}
a = \frac{b^2}{c} \label{eqn:wholeinparts}
\end{equation}

From the equation $a = b + c$ we get \[ \frac{a}{b} = \frac{b}{c} + 1 \] if we now substitute the equation $(\ref{eqn:wholeinparts})$ we get the follow equation \[ \frac{b^2}{c^2} = \frac{b}{c} + 1 \] and if we now let $\Phi = \frac{b}{c}$ we get 
\begin{equation} 
\Phi^2 = \Phi + 1 \label{eqn:goldenquadratic}
\end{equation} 
If we now use the quadratic formula to solve this equation and eliminate the negative root on the grounds that the value must be positive by the greek definition we arrive at the value $\Phi = \frac{1 + \sqrt{5}}{2}$\\

Part b) We now want to show that \[ \Phi = 1+ \cfrac{1}{1+\cfrac{1}{1+\cfrac{1}{1+\cdots}}} \] If we let $x_{n+1} = 1 + \frac{1}{x_{n}}$ and $x_1 = 1$ then this sequence reproduces the continued fraction. We need to show this sequence converges to the $\Phi$. \\
\indent We first want to show that the sequence is bounded $1 \le x_n \le 2$. We will show that $1 < x_n < 2$ for $n \ge 3$. For $x_3 = \frac{3}{2}$ the inequality is true. Now assume the inequality for a give $n > 3$. Then we have the following calculation
\[ 1 < x_n < 2 \implies \frac{1}{2} < x_n < 1 \implies 1 < \frac{3}{2} < 1 + \frac{1}{x_n} < 2  \implies 1 < x_{n+1} < 2\]
This completes the induction for the inequality $1 < x_n < 2$. Now, since we have $x_1 = 1$ and $x_2 = 2$ we actually have the bound $1 \le x_n \le 2$ for all $n$ and the sequence is bounded.\\
\indent We now show that the sequence $(x_n)$ increases for odd $n$ and decreases for even $n$. First consider 
\begin{equation}
 x_{n+2} = 1 + \frac{1}{x_{n+1}} = 1 + \frac{1}{1 + \frac{1}{x_n}} = 1 + \frac{x_n}{x_n + 1} \label{eqn:extendfib}
\end{equation} 

We show that the even terms of the sequence decrease by induction. Since $x_2 = 2$ and $x_4 = \frac{5}{3}$ we have $x_2 > x_4$. Assume that $x_{2n} > x_{2n+2}$ and performing the following calculation shows the induction step
\begin{eqnarray*}
x_{2n} &>& x_{2n+2} \\
x_{2n} x_{2n+2} + x_{2n} &>& x_{2n} x_{2n+2} + x_{2n+2} \\
(x_{2n+2} + 1)x_{2n} &>& (x_{2n} + 1) x_{2n+2} \\
\frac{x_{2n}}{x_{2n} + 1} &>& \frac{x_{2n+2}}{x_{2n + 2} + 1}\\
1 + \frac{x_{2n}}{x_{2n} + 1} &>& 1+ \frac{x_{2n+2}}{x_{2n + 2} + 1}\\
x_{2n+2} &>& x_{2n+4} \quad \text{by equation (\ref{eqn:extendfib})}
\end{eqnarray*}

This shows that the subsequence of even indices decreases. We notice that $x_1 = 1$ and $x_3 = \frac{3}{2}$ so $x_1 < x_3$ and assume that $x_{2n-1} < x_{2n+1}$ and perform the same calculation as above we show that the odd indices subsequence increases. Because both subsequences are monotonic and bounded they both converge. Both subsequences can be considered written as \[x_{n+2} = 1 + \frac{x_n}{x_n + 1}\] with restrictions on the indices. So for example if $n = 2m$ and is even then we have the following value for the limit.
\[ x = \lim_{m \to \infty} x_{2m + 2} = \lim_{m \to \infty}1 + \frac{x_{2m}}{x_{2m} + 1} = 1 + \frac{x}{x + 1} \]
If we multiple both sides by $x + 1$ we get $x^2 + x = x + 1 + x \implies x^2 = x + 1$. So the limit of the subsequence satisfies the golden mean quadratic. Since $x_n \ge 1 > 0$ for all n we take the positive root of the equation. The odd sebsequence has the same limit by the reasoning above. Since both the even and odd subsequences limit to the same value $\Phi$ problem 2 tells us that the full sequence has the property that $\lim_{n \to \infty} x_n = \Phi$. So the infinite fraction has the value of the golden mean.\\

Part c) Now we want to show that $\Phi = \sqrt{1 + \sqrt{1 + \sqrt{1 + \sqrt{1 + \cdots }}}} $%+ \sqrt{1 + \{sqrt{1 + \cdots}}}}$ \\
As in part b by we define a sequence and show that it converges to the expected value.\\
\indent Let $y_n = \sqrt{1 + y_n}$ and $y_1 = 1$. First we show that it is bounded above by 2. Since $y_1 = 1 < 2$ we have the induction base. Now assume that $y_n < 2$ since $y_{n+1} = \sqrt{1 + y_n} < \sqrt{1 + 2} = \sqrt{3} < 2$ we have the complete induction step so $(y_n)$ is bounded above by 2.\\
\indent In a similarly inductive fashion we can show that the sequence is monotonically increasing. For $y_1 = 1$ and $y_2 = \sqrt{2}$ so $y_1 < y_2$. Now assume that $y_n < y_{n+1}$ and perform the following calculation to show the inductive step.
\begin{eqnarray*}
y_n &<& y_{n+1} \\
1 + y_n &<& 1 + y_{n+1} \\
\sqrt{1 + y_n} &<& \sqrt{1 + y_{n+1}} \\
y_{n+1} &<& y_{n+2}
\end{eqnarray*}
Because $(y_n)$ is bounded above and monotonically increasing in converges. This allows us to perform the following calculation
\[ y = \lim_{n \to \infty} y_{n+1} = \lim_{n \to \infty} \sqrt{1 + y_n} = \sqrt{1 + y}  \]
Squaring both sides gives us \[ y^2 = y + 1 \] which is the equation for the golden mean. Because $y_1 = 1$ and the sequence is monotonically increasing we are compelled to take the positive root of this equation and get the derive the fact that $\lim_{n \to \infty} y_n = \Phi$.\\

Part d) Finally we want to show that the sequence $z_{n+2} = z_{n+1} + z_n$ with $z_1 = 1$ and $z_2 = 1$ has the property that $\lim_{n \to \infty} \frac{z_{n+1}}{z_{n}} = \Phi$. If we divide both sides of $z_{n+2} = z_{n+1} + z_n$ with $z_{n+1}$ then we get 
\[ \frac{z_{n+2}}{z_{n+1}} = 1 + \frac{z_n}{z_{n+1}} \]
 If we now define $x_n = \frac{z_{n+1}}{z_n}$ then we have $x_1 = \frac{z_2}{z_1} = 1$ and 
\[ x_{n+1} = 1 + \frac{1}{x_n}\] 
This is indentical to part b so we have 
\[ \lim_{n \to \infty}  \frac{z_{n+1}}{z_n} = \lim_{n \to \infty} x_n = \Phi\]

\indent 
\vspace{15pt}
\begin{flushleft} 
\textbf{Class 18.100B} - Extra Problem 1\\
\rule{500pt}{1pt}\\
\end{flushleft} 

We are being asked to show that if every subsequence of $(x_n)$ has a subsequence that converges to $x$ then $\lim_{n \to \infty} x_n = x$. Since the set of subsequential limits is closed by a theorem in rudin we can find subsequences such that 
\begin{eqnarray*}
\lim_{k \to \infty} x_{m_k} &=& \liminf x_n \\
\lim_{k \to \infty} x_{n_k} &=& \limsup x_n \\
\end{eqnarray*}

Since any subsequence of a convergent sequence converges to the same limit as original sequence we have from the hypothesis that $\liminf x_n = x = \limsup x_n$. From comments made in Problem 4 we see that $\liminf x_n = \limsup x_n \implies \lim_{n \to \infty} x_n = x$.

\end{document}  